#Retrieve the data saved AFTER the profiling practice...... this means data already cleaned

```{r}
# install.packages('cluster')
path <- "path.txt"
path <- readChar(path, file.info(path)$size)
path <- gsub("[\r\n]", "", path)
setwd(path) #set the working directory
df <- read.delim("clean_table_knn.csv",sep = ',',header=T);
df

borrar <- c("group_mPower","group_cSpeed", "group_mSpeed")
df <- df[ , !(names(df) %in% borrar)]
df

var_binarias <- c("Dedicated", "Notebook_GPU", "SLI_Crossfire")
var_cualitativas <- c("Direct_X","Architecture", "Manufacturer", "Memory_Type", "Open_GL", "Shader", "Name", "Resolution_WxH", "Release_Date", "Memory_Bus")


for (i in var_cualitativas){ 
    df[,i] <- as.factor(df[,i])
}

for (i in var_binarias){ 
    df[,i] <- as.factor(df[,i]) 
}
df



```

# HIERARCHICAL CLUSTERING
```{r}
library('cluster')
numericalVariables <- lapply(df, is.numeric)
aux<-df[,unlist(numericalVariables)]
aux

d  <- dist(aux)
h1 <- hclust(d,method="ward.D")  # NOTICE THE COST
plot(h1)

```

```{r}
dissimMatrix <- daisy(df, metric = "gower", stand=TRUE)

distMatrix<-dissimMatrix^2

h2 <- hclust(distMatrix,method="ward.D")  # NOTICE THE COST
plot(h2)

```

# BUT WE ONLY NEED WHERE THERE ARE THE LEAPS OF THE HEIGHT

# WHERE ARE THER THE LEAPS? WHERE WILL YOU CUT THE DENDREOGRAM?, HOW MANY CLASSES WILL YOU OBTAIN?

```{r}
nc = 3

c1 <- cutree(h1,nc)

c1[1:20]

nc = 4

c5 <- cutree(h1,nc)

c5[1:20]


table(c1)
table(c5)
table(c1,c5)


cdg <- aggregate(as.data.frame(aux),list(c1),mean)
cdg

plot(cdg[,1], cdg[,7])
``` 

# LETS SEE THE PARTITION VISUALLY

```{r}

plot(df["Core_Speed"],df["L2_Cache"],col=c1,main="Clustering of credit data in 3 classes")
legend("topright",c("class1","class2","class3"),pch=1,col=c(1:3))



plot(RatiFin,Estalvi)
plot(RatiFin,Estalvi,col=c1,main="Clustering of credit data in 3 classes")
legend("topright",c("class1","class2","class3"),pch=1,col=c(1:3), cex=0.6)

plot(Antiguedad.Trabajo,Estalvi,col=c1,main="Clustering of credit data in 3 classes")
legend("topright",c("class1","class2","class3"),pch=1,col=c(1:3), cex=0.6)
plot(Patrimonio, Ingresos,col=c1,main="Clustering of credit data in 3 classes")
legend("topright",c("class1","class2","class3"),pch=1,col=c(1:3), cex=0.6)
plot(Patrimonio, Antiguedad.Trabajo,col=c1,main="Clustering of credit data in 3 classes")
legend("topright",c("class1","class2","class3"),pch=1,col=c(1:3), cex=0.6)

pairs(dcon[,1:7], col=c1)

```

#plot(FI[,1],FI[,2],col=c1,main="Clustering of credit data in 3 classes")
#legend("topleft",c("c1","c2","c3"),pch=1,col=c(1:3))

# LETS SEE THE QUALITY OF THE HIERARCHICAL PARTITION



Bss <- sum(rowSums(cdg^2)*as.numeric(table(c1)))

Ib4 <- 100*Bss/Tss
Ib4


#move to Gower mixed distance to deal 
#simoultaneously with numerical and qualitative data

library(cluster)

#dissimilarity matrix

actives<-c(2:16)
dissimMatrix <- daisy(dd[,actives], metric = "gower", stand=TRUE)

distMatrix<-dissimMatrix^2

h1 <- hclust(distMatrix,method="ward.D")  # NOTICE THE COST
#versions noves "ward.D" i abans de plot: par(mar=rep(2,4)) si se quejara de los margenes del plot

plot(h1)

c2 <- cutree(h1,4)

#class sizes 
table(c2)

#comparing with other partitions
table(c1,c2)


names(dd)
#ratiFin
boxplot(dd[,16]~c2, horizontal=TRUE)

#plazo
boxplot(dd[,4]~c2, horizontal=TRUE)

#gastos
boxplot(dd[,9]~c2, horizontal=TRUE)

pairs(dcon[,1:7], col=c2)

plot(RatiFin,Estalvi,col=c2,main="Clustering of credit data in 3 classes")
legend("topright",levels(c2),pch=1,col=c(1:4), cex=0.6)

cdg <- aggregate(as.data.frame(dcon),list(c2),mean)
cdg

plot(Edad, Gastos, col= c2)
points(cdg[,4],cdg[,5],pch=16,col="orange")
text(cdg[,4],cdg[,5], labels=cdg[,1], pos=2, font=2, cex=0.7, col="orange")

potencials<-c(3,4,6,7,10,11)
pairs(dcon[,potencials],col=c2)

#Profiling plots
